---
title: "Data import"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(tidytext)
library(lubridate)
```

This is an example of how to do text mining with the Mahabharata and the Ramayana, in versions downloaded from GRETIL.

# Import text
## Read in texts line by line
First we read in the texts line by line and put them in a 'tibble', which is a bit like putting them in a spreadsheet where each row is a line of text.

```{r cars}
mahabharata_raw <- read_lines("data_raw/MBH1-18U.HTM") %>% 
  as_tibble() %>% 
  rename(text = value)

ramayana_raw <- read_lines("data_raw/sa_rAmAyaNa.txt") %>% 
  as_tibble() %>% 
  rename(text = value)
```

# Clean text
## Extract text lines
Now, extract just the text from each.

```{r}
# have a look at the end
mahabharata_raw %>% tail()

mahabharatha_text <- mahabharata_raw %>% 
  slice(82:( n() - 4 )) #keep only from rows 81 until 4 rows before the end

ramayana_text <- ramayana_raw %>% 
  slice(34:n())
```

## Extract out verse information
Each line of the mahabharatha text begins with a verse and line indicator followed by a tab ("\t").
Let's parse that out, then replace those indicators, the tabs, and the break tags ("<BR>") with nothing.

```{r}
mahabharatha_cleaned <- mahabharatha_text %>% 
  mutate(verse_line = str_extract(text, "[^\t]+")) %>% 
  mutate(text_clean = str_replace(text, "[^\t]+", ""),
         text_clean = str_replace(text_clean, "(\t)", ""),
         text_clean = str_replace(text_clean, "<BR>", "")) %>% 
  select(-text)

```

In the ramayana text, some of the lines have verse and line indicators. 
Let's put those in a separate column.
If a line doesn't have a verse and line indicator, we'll give it the one from the following line - or the one after that, if that one's empty too.

```{r}
ramayana_cleaned <- ramayana_text %>%
  filter(text != "") %>%  #drop empty rows
  mutate(verse_line = str_extract(text, r"(R_\d,\d+\.\d+)")) %>% 
  mutate(verse_line = case_when(
    !is.na(verse_line) ~ verse_line,
    is.na(verse_line) & !is.na(lead(verse_line)) ~ lead(verse_line),
    is.na(verse_line) & is.na(lead(verse_line)) & !is.na(lead(verse_line, n = 2)) ~ lead(verse_line, n = 2),
    is.na(verse_line) & is.na(lead(verse_line)) & is.na(lead(verse_line, n = 2)) ~ lead(verse_line, n = 3)
  )) %>% 
  mutate(text_clean = str_replace(text, r"(R_\d,\d+\.\d+)", "")) %>% 
  select(-text)

```



# Save out cleaned text
```{r}
mahabharatha_cleaned %>% 
  write_csv(str_c("data_processed/", today(), "_mahabharatha_cleaned.csv"))

ramayana_cleaned %>% 
  write_csv(str_c("data_processed/", today(), "_ramayana_cleaned.csv"))

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
