---
title: "Data analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)
```

This is an example of how to do text mining with the Mahabharata and the Ramayana, in versions downloaded from GRETIL.

# Read in text
```{r}
texts_to_read <- list.files("data_processed", full.names = TRUE) %>% 
  set_names()

texts <- texts_to_read %>% 
  map_df(read_csv, .id = "document")

texts <- texts %>% 
  mutate(document = case_when(
    str_detect(document, "mahabharatha") ~ "Mahabharatha",
    str_detect(document, "ramayana") ~ "Ramayana",
    str_detect(document, "rgveda") ~ "Rgveda"
  ))

```

Great, let's have a look at how many lines we have from each

```{r}
texts %>% 
  count(document)
```

# Term frequencies & tf-idf
## Term frequency
```{r}
text_word_counts <- texts %>%
  unnest_tokens(word, text_clean) %>% 
  count(document, word, sort = TRUE)

total_words <- text_word_counts %>% 
  group_by(document) %>% 
  summarise(total = sum(n))

text_words <- text_words %>% 
  left_join(total_words) %>% 
  mutate(term_frequency = n / total)

```

Let's try and visualise this

```{r}
text_words %>% 
  group_by(document) %>% 
  arrange(desc(term_frequency)) %>% 
  slice(1:20) %>% 
  ggplot() +
    geom_col(aes(x = reorder(word, term_frequency), y = term_frequency)) + 
    coord_flip() +
    facet_wrap(~document) +
    labs(x = "", y = "Term frequency")
  
```

# Tf-idf
```{r}
word_tf_idf <- text_word_counts %>% 
  bind_tf_idf(word, document, n)

word_tf_idf %>% 
  group_by(document) %>% 
  arrange(desc(tf_idf)) %>% 
  slice(1:20) %>% 
  ggplot() +
    geom_col(aes(x = reorder(word, tf_idf), y = tf_idf, fill = document)) +
    facet_wrap(~document, scales = "free") +
    coord_flip()
    
ggsave("words_tf_idf.png", height = 6, width = 10)
```


# n-grams
## Split text up into bigrams
```{r}
text_bigrams <- texts %>% 
  unnest_tokens(bigrams, text_clean, token = "ngrams", n = 2)

bigram_counts <- text_bigrams %>% 
  count(bigrams, document, sort = TRUE)
```


## Add tf-idf
```{r}
bigram_tf_idf <- bigram_counts %>% 
  bind_tf_idf(bigrams, document, n)

bigram_tf_idf %>% 
  group_by(document) %>% 
  arrange(desc(tf_idf)) %>% 
  slice(1:20) %>% 
  ggplot() +
    geom_col(aes(x = reorder(bigrams, tf_idf), y = tf_idf, fill = document)) + 
    coord_flip() +
    facet_wrap(~document, scales = "free") +
    labs( x = "", title = "tf-idf on bigrams")


```



# topic modelling
See [Julia Silge's (co-author of 'Text Mining With R') wonderful demo on YouTube](https://www.youtube.com/watch?v=evTuL-RcRpc).

See also [this chapter of 'Text Mining With R'](https://www.tidytextmining.com/topicmodeling.html).

# Joining text with additional info
See [the sentiment analysis chapter of 'Text Mining With R'](https://www.tidytextmining.com/sentiment.html).