---
title: "Dashboard example"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
runtime: shiny
---

```{r setup, include=FALSE}
library(shiny)
library(vroom)
library(tidyverse)
library(DT)
library(scales)
library(plotly)

by_line <- vroom("data_processed/texts_combined_line_by_line.csv")
tokenised_by_word <- vroom("data_processed/texts_tokenised_by_words.csv")
term_frequencies <- vroom("data_processed/text_term_frequencies.csv")
text_titles <- term_frequencies %>% distinct(document)
options(shiny.maxRequestSize=30*1024^2)

```

How to Use
===================================== 

### Welcome to the Dashboard!

This is an example of using a flexdashboard to interact with texts downloaded from GRETIL!


For feedback, please contact [ulrik.lyngs\@cs.ox.ac.uk](mailto:ulrik.lyngs@cs.ox.ac.uk).

Enjoy!

<br>
Ulrik Lyngs,\
Human Centered Computing \
Department of Computer Science \
University of Oxford


Overview
===================================== 

Row
-------------------------------------
### Histogram of text lengths
```{r}
term_frequencies %>% 
  group_by(document) %>% 
  summarise(total_words = sum(n)) %>% 
  ggplot() +
    geom_col(aes(x = document, y = total_words, fill = document)) +
    labs(title = "Number of words in texts", x = "", y = "") +
    theme_minimal() +
    guides(fill = FALSE)

```


### Texts
```{r}
term_frequencies %>% 
  group_by(document) %>% 
  summarise(total_words = sum(n)) %>% 
  rename("Number of words" = total_words) %>% 
  knitr::kable()
```


Inspect texts
===================================== 
Inputs {.sidebar data-width=250}
-------------------------------------

```{r}
selectInput("select_text", 
            label = "Select text", 
            choices = text_titles$document)

renderText({
  req(input$select_text)
  
  viewed_text <- text_titles %>% 
    filter(document == input$select_text)
  
  print(str_c(
    "The currently viewed text is:\n",
    viewed_text$document))
})

```

Row
-------------------------------------
### Text - raw and cleaned
```{r}
renderDataTable({
    req(input$select_text)
  
    data <- by_line %>% 
      filter(document == input$select_text) %>% 
      select("Raw text" = text,
             "Cleaned text" = text_clean, 
             `Verse and line` = verse_line)
      
    DT::datatable(data, 
              options = list(
                scrollX="400px",
                scrollY="550px",
                pageLength = 100
    ))
  })

```


### Term frequencies {data-width=300}
```{r}
renderDataTable({
    req(input$select_text)

    data <- term_frequencies %>%
      filter(document == input$select_text) %>% 
      select(word, tf) %>% 
      mutate(tf = round(tf, 5)) %>% 
      rename(term_frequency = tf)

    DT::datatable(data,
              options = list(
                scrollX="400px",
                scrollY="550px",
                pageLength = 100
    ))
  })

```

Count occurrences of words
===================================== 
Inputs {.sidebar data-width=250}
-------------------------------------

This uses ['regular expressions'](https://r4ds.had.co.nz/strings.html#matching-patterns-with-regular-expressions).

A few highlights:

- `[abc]` will match a, b, or c.
- `[^abc]` matches anything *except* a, b, or c.

So if you want to identify various misspellings of 'sakta', you could use `[sś][aā]kta`.


```{r}
textInput("count_word_query", "What word do you want to count?", placeholder = "For example [sś][aā]kta")

```

Row
-------------------------------------
### Count words
```{r}
count_words_data <- reactive({
  req(input$count_word_query)
  
  data <- tokenised_by_word %>%
      filter(str_detect(word, input$count_word_query)) %>%
      group_by(document) %>%
      summarise(num_occurrences = n()) %>%
      arrange(desc(num_occurrences))
})


renderTable({
    req(input$count_word_query)
    
    count_words_data() %>% 
      select("Document" = document, 
             "Number of occurrences" = num_occurrences)
  })

```

Row
-------------------------------------
### Interactive bar chart (each bar is a text)
```{r}
renderPlotly({
  req(input$count_word_query)
  
  gg_test <- count_words_data() %>% 
  
  ggplot() +
    geom_col(aes(x = reorder(document, -num_occurrences),
                 y = num_occurrences,
                 text = document)) +
    labs(y = "Number of occurrences", x = "Text (hover to see info)")

  ggplotly(gg_test, tooltip = c("num_occurrences"))  
})

```



Search in text by line
===================================== 
Inputs {.sidebar data-width=250}
-------------------------------------

This again uses ['regular expressions'](https://r4ds.had.co.nz/strings.html#matching-patterns-with-regular-expressions).

A few highlights:

- `[abc]` will match a, b, or c.
- `[^abc]` matches anything *except* a, b, or c.

So if you want to identify lines with various misspellings of 'sakta', you could use `[sś][aā]kta`.


```{r}
textInput("search_text_query", "What word do you want to search for?", placeholder = "For example [sś][aā]kta")
```


Row
-------------------------------------
### Search texts
```{r}
renderDataTable({
    req(input$search_text_query)
    
    data <- by_line %>% 
      filter(str_detect(text_clean, input$search_text_query)) %>%
      select(line = text_clean, 
             `Document` = document, 
             `Verse and line` = verse_line)
    
    DT::datatable(data, 
              options = list(
                scrollX="400px",
                scrollY="500px"
    ))
  })

```

